Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-07-24 paper/main.tex
structure & some ideas for discussion

\todo[inline]{at the moment I tend to reporting the stability of contrast first,
and then go on to report the primary contrasts for group and individuals; both
has pros and cons}

@@

%Step by step, the reader thus learns to put the paper’s conclusions into the right context.

\paragraph{From Poster}: 1. PPA shows increased activation during non-visual,
complex auditory stimulation that provides incidental spatial information.

2. only minor temporal correlation of regressors of the audio drama \& movie that were not designed for experimental research.

3. but still, alternative contrasts show significant clusters in auditory
cortices.

4. inter-individual differences: for two subjects, an alternative audio-contrast
shows bilaterally significant clusters whereas the primary contrast shows no
significant clusters.

5. audio drama shows bilaterally increased activation in subject 4 in which the
visual localizer shows an unilateral cluster.

6. nevertheless, a  complex auditory stimulus might allow individual
localization of a functionally defined brain region.

7. results of other studies suggest7 the PPA does not exclusively process the
``spatial layout''" but ``contextual associations''.

8. an audio drama might be suitable as ecologically more valid ``localizer'' for
a variety of brain functions.

\subsection{AO Discussion}

Hanke et al. (2014): Compared to an audio-visual movie, this is a stimulus that
leaves a much larger margin for inter-individual differences in imagining
scenery, as well as actors' character and personality traits, while still
preserving the time-locked presentation of information to a listener. At the
same time, an auditory stimulus limits the effect of an attentional focus on the
selection of a subset of simultaneously occurring auditory events, in contrast
to the selection of different parts of the visual field.

aminoff2013: jedoch zu non-spatial stuff: Although the PHC is commonly thought
of as responding to visual stimuli, it has also been found to elicit activity
for auditory stimuli [25,26,30,31] and to respond to odor stimuli [32–34].

Unterschiedliche Qualität der Kontrast: Warum wurde Kontrast 1 als Kontrast 1
gewählt; se\_new se\_old sind recht vague in der Beschreibung der Szene
verglichen mit Bild; Anzahl der Events ergibt auch noch Sinn

setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
dem Wohnwagen ihrer Großmutter" Soundscape macht es häufiger bereits vorher
klar, dass Settingwechsel ist bzw. nicht erst das annotiere Substantiv object
und (room)geo ist vermischt Retrospelinal Cortex ist in Probabilistic maps
krasser als PPA.

Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
Hörbuch??

Contrasts 6-8: words belonging to the categories \texttt{se\_new} and
\texttt{se\_old} were very vague in describing a scene compared to the richness
of a picture. Hence, we assumed smaller probability of successfully isolating
the PPA.

\subsection{AV discussion}
lore ipsum

\section*{General Discussion}

\subsection{Data-driven vs. Analysis-Driven}
"Abfall" einer Film-Messung

\subsection{naturalistic vs. dedicated} how do results (PPA-like response
localization) differ from a standard visual/block-design localizer for:

\subsection{anterior (AO) vs. posterior (AV) PPA}

\subsection{parietal and RSC activations} Story für parietale Aktivierung im
Film -> räuml. Orientierung / Aufmerksamkeit

@@

\subsection{multi-dimensional localizer???}
feasibility of (multi-dimensional) localizer development with naturalistic
stimuli.

>>>>

\todo[inline]{at the moment I think it is better to report the primary contrast
fist and then report the stability of contrast; but that opinion changend twice
already, so here in the text stability of contrast is still reported first}

@@

%Step by step, the reader thus learns to put the paper’s conclusions into the right context.
We used two naturalistic stimuli + annotation + GLM and investigated if we could
isolate the PPA not just in an group average analysis but also on an individual
level. We focus on the audio-only stimulus but performed a analysis for the AV
stimulus as well (not controlling for frame content after cuts).

% Correlation of regressors
Events/Regressors are of little to no correlation despite stimulus was used as
designed for entertainment purposes.

\subsection{Group analysis}

% AO stimulus
% cluster location
AO stimulus isolated spatially concise cluster in anterior part of group overlap mask/roi.
% confounds
2h audio-description offering sufficient events such that many confounding
variables average out (but some anternative contrasts show clusters in auditory
cortices)
% summary statement
This suggest spoken language cues correlate with increased activation in higher
visual areas bilaterally.

% RSC
words to clusters in RSC? -> see Aminoff (20xx). What does the retrosplenial
cortex do?

% theory what the PPA does
\todo[inline]{aminoff2013: jedoch zu non-spatial stuff: Although the PHC is
commonly thought of as responding to visual stimuli, it has also been found to
elicit activity for auditory stimuli [25,26,30,31] and to respond to odor
stimuli [32–34].}
% Mental Imagery Hypothesis
Mental Imagery Hypthesis (s. O'Craven \& Kanwisher, 2000); Lerner (2011), Honey
(2012), Silbert (2014) finden keine ISC in PPA? vgl. auch DataPaper bzgl.
Hörbuch??
% we
We got not task not time to form a vivid mental image; if at all automatic
on-the-fly process; further not task to keep subjects attentive to the stimulus
and espcially spatial cues
% PPA is not visual exclusively
results of other studies suggest7 the PPA does not exclusively process the
``spatial layout''" but ``contextual associations''.
% difference to Aziz
Aziz modeled as boxcar from sentence onset to offset.

% AV stimulus cluster location
AV middle and posterior part of group overlap mask/roi.
% confounds
extending into more posterior regions (which exactly?).
% not controlled frame content
putativ function of those regions?
% number of events?
confounds to not average out in (early) visual areas.
% nevertheless
imo it's cool, that this approach of blindly averaging the frames' content works
at all.

\subsection{stability of contrasts}
% why we did a couple of contrasts
it's not cherry picking of one contrast.
% declining quality of results
contrasts were assumed to be of ``declining'' quality of results which turned
out to be the case.
% decreasing congruency and amount of data
results are kinda stable and not just an accidental finding. Nevertheless,
performance of functional isolation is sensitive to amount of data used and
congruency of contrasts with spatial layout hypothesis.

\subsection{individual analyses}
% AO
We were able to get isolated cluster in anterior part of individual PPA masks in
majority of subjects.
% one threshold for all
Same threshold for all subjects, PPA ROIs were visually / subjectively chosen.
% inter-individual differences
\todo[inline]{which contrasts work better in some subjects?}
% sub-xy
AO yielded bilateral cluster whereas AV stimulus yielded XY and even the
dedicated localizer yieled just one unilateral custer.

% summary statement
Results suggest naturalistic AO stimulus can be used as an non-visual localizer
of a visual area in individual subjects.
% with other words
a  complex auditory stimulus might allow individual localization of a
functionally defined brain region.
% and again other words
an audio drama might be suitable as ecologically more valid ``localizer'' for a
variety of brain functions.
% other example: speech areale
other possibilities: low level features, stuff annotated in speech annotation

% multiple localizer
% PPA is just one example
2h stimulus for just one process is long but chosen cognitive function is just
one aspect that can be investigated with a complex naturalistic stimulus.

% AV
On individual level, mixed results for AV stimulus.
% individual differences
Individual differences when seeing a whole picture with many features vs. stream
of serial auditory information providing incidential cues; spatial attention?
\todo[inlin]{which contrast works better in which subjects?}

% AO vs. AV
AO vs. AV\dots
\todo[inline]{Hanke et al. (2014): Compared to an audio-visual movie, this is a
    stimulus that leaves a much larger margin for inter-individual differences
    in imagining scenery, as well as actors' character and personality traits,
    while still preserving the time-locked presentation of information to a
    listener. At the same time, an auditory stimulus limits the effect of an
    attentional focus on the selection of a subset of simultaneously occurring
    auditory events, in contrast to the selection of different parts of the
visual field}.

\subsection{shortcommings}

% spatial cues can belong to different categories
setting\_new ist häufig vermischt mit anderer Kategorie "ein Arzt", "ein alter
Film", "auf einer Straße", "im Fernsehen", "die drei Jungs", "die zwei im Bett",
"Jenny als Teenager", "Forrest vor einem Buffet", "Kennedy", "Jenny kommt aus
dem Wohnwagen ihrer Großmutter"
% soundsscapes makes change of setting obvious before narrator kicks in
Soundscape macht es häufiger bereits vorher klar, dass Settingwechsel ist bzw.
nicht erst das annotiere Substantiv object und (room)geo ist vermischt
Retrospelinal Cortex ist in Probabilistic maps krasser als PPA.

% se_new and se_old
especially relevant for contrasts 6-8: words belonging to the categories
\texttt{se\_new} and \texttt{se\_old} were very vague in describing a scene
compared to the richness of a picture. Hence, we assumed smaller probability of
successfully isolating the PPA.

\subsection{open question: anterior (AO) vs. posterior (AV) PPA}

@@

\subsection{re-use of existing data for new, independent research questions}
there is more in a complex naturalistic stimulus.
